Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-16 papers/B1555_EdgeOn/B1555_letter.tex
Figures display now

\documentclass[useAMS,usenatbib]{mn2e}

% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Jen-Wei Hsueh and A. N. Other]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$University of California, Davis, Davis 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{figure*}
\begin{minipage}{140mm}
%\includegraphics[width=84mm]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
\end{minipage}

@@

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
%
\label{fig:merlin}}
\end{figure}

@@

>>>>

%\documentclass[useAMS,usenatbib]{mn2e}
\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{graphicx}
% If your system does not have the AMS fonts version 2.0 installed, then
% remove the useAMS option.
%
% useAMS allows you to obtain upright Greek characters.
% e.g. \umu, \upi etc.  See the section on "Upright Greek characters" in
% this guide for further information.
%
% If you are using AMS 2.0 fonts, bold math letters/symbols are available
% at a larger range of sizes for NFSS release 1 and 2 (using \boldmath or
% preferably \bmath).
%
% The usenatbib command allows the use of Patrick Daly's natbib.sty for
% cross-referencing.
%
% If you wish to typeset the paper in Times font (if you do not have the
% PostScript Type 1 Computer Modern fonts you will need to do this to get
% smoother fonts in a PDF file) then uncomment the next line
% \usepackage{Times}

@@

\title[Beware the Effect of Edge-on Disks]{Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375}
\author[Hsueh et al.]{Jen-Wei Hsueh$^{1}$\thanks{E-mail:
email@address (AVR); otheremail@otheraddress (ANO)} and A. N.
Other$^{2}$\footnotemark[1]\thanks{This file has been amended to
highlight the proper use of \LaTeXe\ code with the class file.
These changes are for illustrative purposes and do not reflect the
original paper by A. V. Raveendran.}\\
$^{1}$University of California, Davis, Davis 95616, USA\\
$^{2}$Building, Institute, Street Address, City, Code, Country}
\begin{document}

@@

\begin{figure*}
\begin{minipage}{140mm}
\includegraphics[width=140mm]{B1555_gallery.eps}
\caption{High-resolution multiband imaging of the B1555+375 lens system.
All of the panels are 3\farcs7 on a side, and for each panel the scale bar 
represents 1\arcsec.  From left to right the figures show data from
HST/WFPC2 in the F555W band, HST/WFPC2 in the F814W band, HST/NICMOS/NIC2
in the F160W band, and Keck AO imaging in the $K^\prime$ band.}
%
\end{minipage}

@@

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system with MERLIN radio observation overlaid.
%
\label{fig:merlin}}
\end{figure}

@@

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}
